Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-09 inc/photocathode/este/este.tex
more tweaks to photocathode section

In this section, we show that, at least for thermionic emission, the effective mass $m^*$ of the electronic state from which the electron was emitted affects the rms transverse momentum; that is, the expression for $\Delta p_{\smallT}$ developed in Refs. \cite{dowell_quantum_2009} and \cite{jensen_emittance_2010} for thermionic electron emission should be rewritten to read $\sqrt{m^* k_B T_e}$, where $T_e$ is the temperature of the emitting electron distribution and $k_B$ is Boltzmann's constant.
Direct observation of the transverse momentum distribution for excited-state thermionic emission (ESTE) from GaSb and InSb, two similar III-V zincblende semiconductors, demonstrates the $m^*$ dependence.
Simulations of the experiment using our extended analytical Gaussian (AG) model of electron pulse propagation (see Section \ref{sec:external_forces}) are in close agreement with the data.

>>>>

Recent experiments in our group have come to change our understanding of several photoemission processes, once thought to be well understood \cite{berger_excited_2012}.
Indeed while this knowledge has been commonplace in other fields, such as angle-resolved photoemission spectroscopy (ARPES) \cite{himpsel_angle-resolved_1983}, to our knowledge the effect has not been considered for electron beam generation.
In this section, we show that, at least for thermionic emission, the effective mass $m^*$ of the electronic state from which the electron was emitted affects the rms transverse momentum; that is, the expression for $\Delta p_{\smallT}$ developed in Refs. \cite{dowell_quantum_2009} and \cite{jensen_emittance_2010} for thermionic electron emission should be rewritten to read $\sqrt{m^* k_B T_e}$, where $T_e$ is the temperature of the emitting electron distribution and $k_B$ is Boltzmann's constant.
Direct observation of the transverse momentum distribution for excited-state thermionic emission (ESTE) from GaSb and InSb, two similar III-V zincblende semiconductors, demonstrates the $m^*$ dependence.
Simulations of the experiment using our extended analytical Gaussian (AG) model of electron pulse propagation (see Section \ref{sec:external_forces}) are in close agreement with the data.

### 2013-04-09 inc/photocathode/future.tex
more tweaks to photocathode section

For direct single-photon photoemission, we would therefore also expect to require that the expression describing the rms transverse momentum to be written as $\Delta p_{\smallT} = \sqrt{m^* ( \hbar \omega - \Phi ) / 3 }$.
Efforts are currently underway to determine if this is indeed the case using a variety of metal photocathodes and the $\sim$4ps, 261nm laser radiation source.
In an upcoming publication, we will show that the dependence of $\Delta p_{\smallT}$ on the electron effective mass may be extended to simple planar metal photocathodes --- thus potentially allowing for the future development or discovery of a robust, high brightness photocathode material.
For a selection of single-crystal and polycrystalline photocathodes, we will show that the simulation, incorporating $m^*$, is in good agreement with our direct measurements of $\Delta p_{\smallT}$.
We will also discuss the effect of laser-induced heatingon $\Delta p_{\smallT}$ of the electron distribution in the photocathode during photoemission, which may limit the attainable pulsed electron source brightness at the desired high peak pulse current densities.

>>>>

For direct single-photon photoemission, we would therefore also expect to require that the expression describing the rms transverse momentum (\ref{eq:jensen_eta}, Refs. \cite{dowell_quantum_2009} and \cite{jensen_emittance_2010}) to be written as $\Delta p_{\smallT} = \sqrt{m^* ( \hbar \omega - \Phi ) / 3 }$.
Efforts are currently underway to determine if this is indeed the case using a variety of metal photocathodes and the $\sim$4ps, 261nm laser radiation source.
In an upcoming publication, we will show that the dependence of $\Delta p_{\smallT}$ on the electron effective mass may be extended to simple planar metal photocathodes --- thus potentially allowing for the future development or discovery of a robust, high brightness photocathode material.
For a selection of single-crystal and polycrystalline photocathodes, we will show that the simulation, incorporating $m^*$, is in good agreement with our direct measurements of $\Delta p_{\smallT}$.
We will also discuss the effect of laser-induced heatingon $\Delta p_{\smallT}$ of the electron distribution in the photocathode during photoemission, which may limit the attainable pulsed electron source brightness at the desired high peak pulse current densities.

### 2013-04-09 inc/photocathode/setup/setup.tex
more tweaks to photocathode section

To address this need, I have experimented with several candidate photocathodes, which belong to several different categories of photoemission processes.
In this chapter, I will present an example of each of these different processes, and discuss its prospects for reducing the transverse emittance and therefore utility as an electron source for UEM.

>>>>

To address this need, I have experimented with many candidate photocathodes, which implement a variety of different photoemission processes.
In this chapter, I will present an example of several of these different processes, discuss its prospects for reducing the transverse emittance and finally assess its utility as an electron source for UEM.
I will then outline some future research directions that the group at UIC will continue to pursue.
Since this is the most active current field in our group's reseach, some very new results are presented near the end of the chapter and future plans are evolving.
